---
title: "Clustering Mezcla Gaussiana"
author: "JairES"
format: html
editor: visual
---

## Mclust

Se utiliza la librería mclust para clustering/clasificación a partir de modelos de mezcla Gaussiana.

## Criterio de Información Bayesiana

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
datos = read.csv("")
datos_prueba = datos[,- 1]
BIC2 <- mclustBIC(datos_prueba,G = 6:15,modelNames = c("EEI","EEV","EEE"))
mod1_2 <- Mclust(datos, x = BIC2)
s = summary(mod1, parameters = TRUE)
# 998 renglones y 978 columnas rellenar por renglones
clasificacion = s$classification
clasificacion = clasificacion[-((length(clasificacion) - 35): length(clasificacion))]
clasificacion = as.numeric(clasificacion)
matriz_clasificacion = matrix(as.array(clasificacion), nrow = 998, ncol = 978, byrow = TRUE)
library(raster)
raster_data <- raster(matriz_clasificacion)
raster_extent <- extent(raster_data)
color_palette <- terrain.colors(100) # Puedes ajustar el n´umero de colores seg´un tu preferencia
plot(raster_data, col=rainbow(15), main="Raster pv_refri1.tif")
plot(shapefile, add=TRUE, col="white", border="red")
writeRaster(raster_data, "C:\\Users\\Usuario\\Desktop\\Eduardo Alanis(Servicio)\\Cosas Realizadas\\
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
